Praise the people or praise the place? Upper tail human capital in electrifying Sweden

### 2024-01-24 index.qmd
add favicon

---
title: "Praise the people or praise the place? Upper tail human capital in electrifying Sweden"
subtitle: "Midway Seminar - 24-01-2024"
author: 
  - "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview_wide.png"
  data-background-position: "bottom 10"
  data-background-size: "90%"
  data-background-opacity: "0.4"
bibliography: bibliography.bib
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com/content/research.html)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    include-in-header: 
        - text: <link rel = "shortcut icon" href = "assets/favicon.ico" />

>>>>

---
title: "Praise the people or praise the place? Upper tail human capital in electrifying Sweden"
subtitle: "Midway Seminar - 24-01-2024"
author: 
  - "Jonathan Jayes  - Lund University"
title-slide-attributes:
  data-background-image: "assets/preview_wide.png"
  data-background-position: "bottom 10"
  data-background-size: "90%"
  data-background-opacity: "0.4"
bibliography: bibliography.bib
format: 
  revealjs:
    code-overflow: wrap
    width: 1600
    height: 900
    fig-align: center
    default-image-extension: svg
    footer: "[{{< fa house >}}](https://interludeone.com/content/research.html)"
    slide-number: c
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    include-in-header: 
        - text: <link rel = "shortcut icon" href = "assets/favicon.ico" />
favicon: "assets/favicon.ico"
